---
title: "STAT 218 Lab Assignment 3"
subtitle: "Week 6 Lecture 4 Lab 3"
author: 
  - "Team Member 1: NAME HERE"
  - "Team Member 2: NAME HERE"
  - "Team Member 3: NAME HERE"
date: today
date-format: "MMMM D[<sup style='font-size:65%;'>th</sup>], YYYY"
format: pdf
execute:
  echo: true
---

## Lab Assignment 3

Please run the code chunk below to download the necessary package you need.

```{r}
#| include: false
install.packages("infer" , repos = "http://cran.us.r-project.org")
```

Remember, we need to use library functions to be able to tell R which package we want to use right now. Please run the code chunk below too.

```{r}
#| output: false
library(infer)
library(tidyverse)
library(palmerpenguins)
data("penguins") 
```

**NOTE:** Please ignore `penguins_raw` data for this class and USE `penguins` for this assignment.

# One Sample *t* test

In this case, we will use `penguins` data set.

**Example 1:** Imagine that you are a biologist studying penguins, particularly their bill lengths. Previous studies have hypothesized that the population mean bill length of penguins is 40 mm. You collect a random sample of 344 penguins and measure and record their bill lengths in millimeters.

**Question 1.1. What is the research question of this study?**

Type your answer here.

**Question 1.2. What type of variable do we have in this study?**

Type your answer here.

**Question 1.3. Check the lecture slides and please list the assumptions required for this test and check the assumption of normality for this study. Interpret the assumptions overall.**

*Random Sampling:* Explain here.

*Independence of Observation:* Explain here.

*Normality Distribution:* Explain here.

```{r}
# Type your codes here to check normality by using histogram. Find ggplot codes from our previous data viz lab slides for creating a HISTOGRAM.
```

Interpret your histogram here.

Interpret the assumptions overall and type your reasoning.

**Directions for Question 1.4:** Conduct a one sample$t$-test to investigate whether the bill length of the penguins differs from the test value of 40 mm. Answer the questions given below.

**Question 1.4.1 Write out the null & the alternative hypotheses within the context of this study:**

Type your answer here.

**Question 1.4.2. Compute test statistic by running the code chuck below and explain what you see in the output.**

```{r}
t_test(penguins, response = bill_length_mm, mu = 40)

```

Type your answer here.

**Question 1.4.3. Draw conclusion and write a conclusion statement. Include p-value and confidence interval.**

Type your answer here.

# Independent Samples *t* test

In this case, we will use again `penguins` data set.

**Example 2:** Now, you're curious about the difference in the body mass of penguins based on their sex. You hypothesize that body mass varies between different sexes. To test your hypothesis, you collect a random sample of 344 penguins, measure their body mass, and record their sex.

**Question 2.1. What is the research question of this study?**

Type your answer here.

**Question 2.2. What type of variables do we have in this study?**

Type your answer here.

**Question 2.3. Again check the lecture slides and please list the assumptions required for this test and check the assumption of normality for this study. Interpret the assumptions overall.**

*Random Sampling:* Explain here.

*Independence of Observation:* Explain here.

*Normality Distribution:* Explain here.

```{r}
ggplot(data = na.omit(penguins),
       aes(x = body_mass_g)) +
  geom_histogram() +
  facet_wrap(~sex)
```

Interpret the assumptions and type your reasoning.

**Directions for Question 2.4: Conduct an independent samples** $t$-test to investigate whether the body mass of penguins differs between different sexes.

**Question 2.4.1 Write out the null & the alternative hypotheses within the context of this study:**

Type your answer here.

**Question 2.4.2. Compute test statistic by running the code chuck below and explain what you see in the output.**

```{r}
t_test(x = penguins, 
       formula = body_mass_g ~ sex, 
       order = c("male", "female"),
       alternative = "two-sided",
       conf_level = 0.90)
```

Type your answer here.

**Question 2.4.3. Explain what each function/argument does in this question.**

`t_test`: Type your answer here.

`formula`:Type your answer here.

`order`: Type your answer here.

`alternative`: Type your answer here.

`conf.level`: Type your answer here.

**Question 2.4.4. Draw conclusion and write a conclusion statement. Include p-value and confidence interval interpretations.**

Type your answer here.

# Paired Samples *t* test

In this assignment, we will work with an external data set. Make sure download the dataset (stream.csv) from Canvas as well.

Let's use `library` function and load the data sets that we will use today.

```{r}
#| output: false
library(tidyverse)
stream <- read_csv("stream.csv")
```

**Example of a Case:** Pollutants in a stream may accumulate or attenuate as water flows down the stream. In a study to monitor the accumulation and attenuation of fecal contamination in a stream running through cattle rangeland, monthly water specimens were collected at two locations along the stream over a period of 21 months.

The data set `stream` the total coliform count (MPN/100ml) for a water specimen.

**Question 3.1. What is the research question of this study?**

Type your answer here.

**Question 3.2. What type of variables do we have in this data set? Quantitative or categorical?**

*sample:*

*date:*

*upstream:*

*downstream:*

*difference:*

**Question 3.3. Please list the assumptions required for this test and check the assumption of normality for this study. Interpret the assumptions overall.**

*Random Sampling:* Explain here.

*Independence of Observation:* Explain here.

*Normality Distribution:* Explain here.

-   *This output is from a calculation of Shapiro-Wilk test. We generally use Shapiro-Wilk test for relatively smaller sample size because visuals can be misleading in smaller sample sizes. Please interpret Shapiro-Wilk* $p$-value.

    Shapiro-Wilk normality test

data: stream\$Difference W = 0.9641, p-value = 0.6022

Type your answer here.

**Directions of Question 3.4: Perform a paired sample** $t$-test to assess whether the mean total coliform count is consistent across the two locations.

**Question 3.4.1 Write out the null & the alternative hypotheses within the context of this study:**

Type your answer here.

**Question 3.4.2. Compute test statistic by running the code chuck below and explain what you see in the output.**

```{r}
t.test(stream$upstream, stream$downstream, paired = TRUE)
```

Type your answer here.

**Question 3.4.3: Run the code chuck below again and explain what you see in the output.**

```{r}

t.test(stream$difference, mu = 0)

```

Type your answer here.

**Question 3.4.4. Compare and contrast how the codes in Question 3.4.2 and Question 3.4.3 work. Comment on the p-value, test statistic, and confidence interval. If they produce the same results, explain what the two codes did differently.**

Type your answer here.

**Question 3.4.5. Draw conclusion and write a conclusion statement.**

Type your answer here. Comment on p-vale and confidence interval.
