---
title: "Ch. 6 & Ch. 7: Review of $t$-tests"
subtitle: "STAT 218 - Week 6, Lecture 4 Lab 3"
format: 
  revealjs:
      theme: simple
      slide-number: true
      chalkboard: true
---


# What Have We Learned So Far?

## 
### A Snapshot

::: {style="font-size: 30px"}


- **Inferential Statistics** makes predictions and draws conclusions about populations based on sample data.
  - We saw different types of t-tests:
    - __One sample t-test:__ compares a sample mean to a known or hypothesized population mean.
    - __Independent samples t-test:__ compares means of two independent groups.
    
- We'll see these tests today.
    

:::


# Hypothesis Testing Steps

## 
#### Introduction 

:::{.callout-important}

We can summarize hypothesis testing in four steps (if we use theory-based approach):

1. Construct the Hypotheses of $H_0$ and $H_A$.
2. Check the validity conditions/assumptions  
3. Compute test statistic, find the _p_-value and confidence interval (Interpreting R Output)
4. Draw conclusion.

:::

## 
### To-do List Before Start - I
::: {style="font-size: 26px"}
- Assign your roles.
  
_Project Manager:_

  - Follow the slides and give directions to the coder and note taker.
  - Facilitate communication within the group and with the instructor.

_Note Taker:_

  - Take notes on key findings, insights, and interpretations derived from the data and analyses.

_Coder:_

  - Lead the coding efforts, writing and managing the R scripts.
  - Ensure code quality, functionality, and documentation standards are met.

:::

## 
### To-do List Before Start - II

::: {style="font-size: 26px"}

1. Download the assignment from course website (Lab Assignment 3).  

2. Follow the instructions on this slideshow to complete the assignment.    

:::





# Setting the Scene

## 
### Downloading Necessary Packages 

- To begin with, we need `infer` package to conduct _t_ tests. 
- Let's run the code chunk in our lab assignment 3 file and load `infer` package by using `install.packages()` function.


```{r}
#| eval: false
#| echo: true
#| output: false
install.packages("infer")
```


##
### Running Library Functions and Loading Datasets


After loading that package, let's run `library` functions and load the data set that we will use today.

```{r}
#| output: false
#| echo: true
library(tidyverse)
library(infer)
library(palmerpenguins)
data("penguins") 
```



# One Sample $t$-test

## 

__Example of a Case:__ 

Imagine that you are a biologist studying penguins, particularly their bill lengths. Previous studies have hypothesized that the population mean bill length of penguins is 40 mm. You collect a __random sample__ of 344 penguins and measure and record their bill lengths in millimeters.

Perform a __one sample $t$-test__ to investigate whether the bill length of the penguins differs from the test value of 40 mm. 


##
### Instructions

Open the assignment file and answer the following questions.

<br>

__Question 1. What is the research question of this study?__

Type your answer in the assignment file.

<br>

__Question 2. What type of variable is used in this study?__

Type your answer in the assignment file.


## 
### Assumptions - Validity Conditions
::: {style="font-size: 28px"}

- It is always important to check first whether the conditions are reasonable in a given case.

- Here is the list of conditions that we should be aware of for one sample $t$-test.

__1) Random Sampling:__ the data can be regarded as coming from independently chosen random sample,

__2) Independence of Observations:__ the observations should be independent (One observation does not influence another.). If (1) You randomly sample individuals from a very large population, and (2) Each selection does not affect another, then observations are typically independent. 

__3) Normality Assumption:__ You should have either symmetric (approximate normality) population distribution  
OR   
n > 30 (some references says 20) AND sample distribution not strongly skewed.

:::

## 
### Normality Assumption - I
::: {style="font-size: 28px"}

- If the only source of information is the data at hand, then normality can be roughly checked.  

  - Unfortunately, for a small or moderate sample size, this check is fairly rudimentary.
  - If the sample is large, then the visual plots (histogram) give us good information; 
    - However, if $n$ is large, the requirement of normality is less important anyway due to the Central Limit Theorem.
- In any case, a rudimentary check is better than none, and every data analysis should begin with inspection of a graph of the data, with special attention to any observations that lie very far from the center of the distribution.

:::


## 
#### Question 3. Checking the Normality Assumption

<br>

- Check your sample size first! 
  - sample size is large, so we can check visual plots.
- _Direction:_ Please create a histogram to check the normality.


## 
### Question 4. Interpreting the Output


```{r}
#| echo: true
#| output: true
t_test(penguins, response = bill_length_mm, mu = 43)
```

::: {style="font-size: 28px"}

__Conclusion:__ _Type your hypothesis testing conclusion to your assignment file!_

__Confidence Interval:__ _Type your confidence interval statement to your assignment file!_

:::

# Independent Samples $t$-test

## 
__Example of a Case:__ 

Now, you're curious about the difference in the body mass of penguins based on their sex. You hypothesize that body mass varies between different sexes. To test your hypothesis, you collect a random sample of 344 penguins, measure their body mass, and record their sex.

Perform an __independent samples $t$-test__ to investigate whether the body mass of penguins differs between different sexes.

##
### Instructions

Continue with the assignment file and answer the following questions.

__Question 1. What is the research question of this study?__

Type your answer in the assignment file.

__Question 2. What type of variable is used in this study?__

Type your answer in the assignment file.

## 
### Assumptions - Validity Conditions
::: {style="font-size: 28px"}

- It is always important to check first whether the conditions are reasonable in a given case.

- Here is the list of conditions that we should be aware of for independent samples $t$-test.

__1) Random Sampling:__ the data can be regarded as coming from independently chosen random sample(s),

__2) Independence of Observations:__ the observations should be independent (One observation does not influence another.).If (1) You randomly sample individuals from a very large population, and (2) Each selection does not affect another, then observations are typically independent. 

__3) Normality Assumption:__ n > 20 __for each group__ AND sample distributions should not be strongly skewed.

:::


## 
### Question 3. Checking the Normality Assumption

- Check your sample size first! 
  - sample sizes are large, so we can check visual plots (e.g., histogram) for each group.
  

## 
### Question 3. Creating Two Histograms for Normality

```{r}
#| echo: true
#| output: true
ggplot(data = na.omit(penguins),
       aes(x = body_mass_g)) +
  geom_histogram(binwidth = 100) +
  facet_wrap(~sex)
```

## 
### Question 4. Interpreting the Output


```{r}
#| echo: true
#| output: true
t_test(x = penguins, 
       formula = body_mass_g ~ sex, 
       order = c("male", "female"),
       alternative = "two-sided",
       conf_level = 0.90)
```

::: {style="font-size: 28px"}

__Conclusion:__ _Type your hypothesis testing conclusion to your assignment file!_

__Confidence Interval:__ _Type your confidence interval statement to your assignment file!_

:::


